---
title: "final_project"
author: "Kaitlin Swinnerton"
date: "11/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
# load packages 
library(foreign)
library(data.table)
library(knitr)

# add more packages
library(sandwich)
library(lmtest)
library(stargazer)
library(randomizr)

# more more more
library(car)
```

Load data

```{r}
d <- fread("data/data_final.csv")
d = data.table(d)
head(d)
```
Data description:
  Baseline affect measures from the DASS-21: 'depression_0', 'anxiety_0', 'stress_0'
    https://www.psytoolkit.org/survey-library/depression-anxiety-stress-dass.html
  
  Stress measures from the Perceived Stress Scale: 'pss_score_0', 'pss_score_1', 'pss_score_2'
    https://www.psytoolkit.org/survey-library/stress-pss.html

  Mental Rotation Task: at 0, 1, 2 weeks
    https://www.psytoolkit.org/experiment-library/mentalrotation.html
    'MR_reaction_times' : trial specific reaction time - time taken to answer question
    'MR_correct' : trial specific accuracy
    'MR_mean_reaction_time' : average time spent on question
    'MR_percent_correct' : accuracy for whole task
  
  Go/No-go Task: at 0, 1, 2 weeks
    https://www.psytoolkit.org/experiment-library/go-no-go.html
    'gng_commission_errors_0': number of commision errors (trials where space bar was hit when no-go was shown)
    'gng_mean_hit_rxn_times_0': average reaction time for 'hit' trials - (trials where space bar was hit when go was shown)
     
  Time on Survey: at 0,1,2 weeks
    'TIME_start_': tiem started survey
    'TIME_end_', : time finished survey
    'TIME_total_', : total time on survey
    
  Self Report Activity Measures at 1 and 2 weeks 
    'activity_count_1': number of times assigned activity was completed in last week
    'start_day_1': only taken on week 1, whether participants completed first task on Monday, Tuesday, or Other
    'TOA_mon_', 'TOA_tue_', 'TOA_wed_', 'TOA_thurs_', 'TOA_fri_1': time of day avticity was completed (or Not completed)
       
  Indicator variables for completing surveys
    'completed_intake', 'completed_w1', 'completed_w2',
    'total_surveys_completed': total number of surveys completed


```{r}
colnames(d)
```

Randomization check
```{r}

d[Group == 0 | Group == 1, .("mean age" = mean(age, na.rm=TRUE), "percent female" = mean(female, na.rm=TRUE), 
      "meditated before" = mean(meditated_before, na.rm=TRUE),
      "baseline depression" = mean(depression_0, na.rm=TRUE), 
      "baseline_stress" = mean(stress_0, na.rm=TRUE),  "baseline_anxiety" = mean(anxiety_0, na.rm=TRUE)),
  by = Group]
```


```{r}
tail(d)
```



```{r}

calc_slopes = function(var, slope_list){
  for (i in c(1:127)){
    X = c(0,1,2)
    y = c( d[[paste(var, '_0', sep='')]][i], d[[paste(var , '_1', sep='')]][i],
           d[[paste(var , '_2', sep='')]][i])
    if (is.na(mean(y))){
      slope_list[i] = NA
    }
    else{
    model = lm(y~X )
    slope_list[i] = coefficients(model)[2]
    }
  }
  return (slope_list)
}

empty_slopes = c(rep(NA, 127))

d[, pss_slopes := calc_slopes('pss_score', empty_slopes), ]
d[, mr_accuracy_slopes := calc_slopes('MR_percent_correct', empty_slopes), ]
d[, mr_rxn_slopes_slopes := calc_slopes("MR_mean_reaction_time", empty_slopes), ]
d[, gng_commission_errors_slopes := calc_slopes('gng_commission_errors', empty_slopes), ]
d[, gng_rxn_slopes := calc_slopes("gng_mean_hit_rxn_times", empty_slopes), ]

d[, hist(pss_slopes), ]
d[, hist(mr_accuracy_slopes), ]
d[, hist(mr_rxn_slopes_slopes), ]
d[, hist(gng_commission_errors_slopes), ]
d[, hist(gng_rxn_slopes), ]


```

```{r}
p1 <- hist(d[Group == 0, pss_slopes], )                     
p2 <- hist(d[Group == 1, pss_slopes])                      
plot( p2, col=rgb(0,0,1,1/4)  , main = "Histogram of Change in Perceived Stress", xlab = "Change in Perceived Stress") 
plot( p1, col=rgb(1,0,0,1/4), add=T)
legend("topright", c("Meditation", "Puzzles"), col=c(rgb(0,0,1,1/4), col=rgb(1,0,0,1/4)), lwd=10)

```

```{r}
p1 <- hist(d[Group == 0, mr_accuracy_slopes], )                     
p2 <- hist(d[Group == 1, mr_accuracy_slopes])                      
plot( p2, col=rgb(0,0,1,1/4)  , main = "Histogram of Change in Mental Rotation Accuracy", xlab = "Change in Mental Rotation Accuracy") 
plot( p1, col=rgb(1,0,0,1/4), add=T)
legend("topright", c("Meditation", "Puzzles"), col=c(rgb(0,0,1,1/4), col=rgb(1,0,0,1/4)), lwd=10)

```
```{r}
p1 <- hist(d[Group == 0, mr_rxn_slopes_slopes], )                     
p2 <- hist(d[Group == 1, mr_rxn_slopes_slopes])                      
plot( p2, col=rgb(0,0,1,1/4)  , main = "Histogram of Change in Mental Rotation Reaction Time", xlab = "Change in Mental Rotation Reaction Time") 
plot( p1, col=rgb(1,0,0,1/4), add=T)
legend("topright", c("Meditation", "Puzzles"), col=c(rgb(0,0,1,1/4), col=rgb(1,0,0,1/4)), lwd=10)

```
```{r}
p1 <- hist(d[Group == 0, gng_commission_errors_slopes], )                     
p2 <- hist(d[Group == 1, gng_commission_errors_slopes])                      
plot( p2, col=rgb(0,0,1,1/4)  , main = "Histogram of Change in Go/No-go Commission Errors", xlab = "Change in Go/No-go Commission Errors") 
plot( p1, col=rgb(1,0,0,1/4), add=T)
legend("topright", c("Meditation", "Puzzles"), col=c(rgb(0,0,1,1/4), col=rgb(1,0,0,1/4)), lwd=10)

```

```{r}
p1 <- hist(d[Group == 0, gng_rxn_slopes], )                     
p2 <- hist(d[Group == 1, gng_rxn_slopes], )                      
plot( p2, col=rgb(0,0,1,1/4)  , main = "Histogram of Change in Go/No-go Reaction Time", xlab = "Change in Go/No-go Reaction Time") 
plot( p1, col=rgb(1,0,0,1/4), add=T)
legend("topright", c("Meditation", "Puzzles"), col=c(rgb(0,0,1,1/4), col=rgb(1,0,0,1/4)), lwd=10)

```


```{r}
scatterplotMatrix(d[,c("pss_score_0","stress_0", "anxiety_0", "depression_0"),],
                  diagonal=list(method ="histogram", breaks="FD"), 
                  main = "Baseline Affect Measures")
```
```{r}
scatterplotMatrix(d[,c("stress_0", "pss_score_0", "pss_score_1", "pss_score_2", "pss_slopes"),],
                  diagonal=list(method ="histogram", breaks="FD"), 
                  main = "Stress Measures")
```
```{r}
scatterplotMatrix(d[ Group == 0, c("stress_0", "pss_score_0", "pss_score_1", "pss_score_2", "pss_slopes"), ],
                  diagonal=list(method ="histogram", breaks="FD"), 
                  main = "Stress Measures")
```
```{r}
scatterplotMatrix(d[ Group == 1, c("stress_0", "pss_score_0", "pss_score_1", "pss_score_2", "pss_slopes"), ],
                  diagonal=list(method ="histogram", breaks="FD"), 
                  main = "Stress Measures")
```


```{r}
d[ , .("completed intake" = mean(completed_intake), "complted week 1" = mean(completed_w1), 
       "complted week 2" = mean(completed_w2), "average completed surveys" = mean(total_surveys_completed)), Group]
```

```{r}
d[ , .("completed intake" = sum(completed_intake), "complted week 1" = sum(completed_w1), 
       "complted week 2" = sum(completed_w2), "average completed surveys" = mean(total_surveys_completed)), Group]
```


```{r}
d[ total_surveys_completed == 3, .N, Group]
```




